Untitled

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
section 2 of disc

In this paper, we:

(i) describe a framework comprised of:
  - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of ready4 modules, datasets and analyses.

(ii) provide a worked example of how we used the framework to develop and apply ready4 modules for utility mapping.

>>>>

In this paper, we describe:

(i) the ready4 framework, that is comprised of:
  - a set of standards for implementing an accountable, reusable and updatable MOSHEM; and
  - a modelling toolkit (online repositories and software) for applying those standards to the authoring of MOSHEM modules, datasets and analyses; and

(ii) how we used the ready4 framework to develop and apply modules for utility mapping.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Discussion.Rmd
section 2 of disc

In this article we introduced a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health. We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of ready4. We also provided an overview of an initial set of ready4 modules developed with the framework to implement a utility mapping study. We reviewed the modules, datasets and analyses generated by that study against framework standards.

The strengths, limitations and issues raised by this work can be discussed in terms of relevance to future development of ready4, to health economists interested in undertaking other MOSHEMS and to funders of health economic research.

## Implications for the development of the ready4 MOSHEM
One of the main novel contributions of the framework we have developed is that it declares an explicit set of standards for the implementation and use of a MOSHEM. A practical benefit of specifying these standards is that it enabled us to develop a modelling toolkit to partially automate workflows for authoring, documenting and disseminating ready4 modules, datasets and analyses. The modelling toolkit's practical utility has been demonstrated through its application in creating all ready4 components used in a utility mapping study [@Hamilton2021.07.07.21260129] and the automation it facilitates makes the development and curation of a large and growing number of ready4 digital assets more tractable. The interoperability of the ready4 modules we have developed today is demonstrated in multiple example literate programs on the ready4 documentation website [@rfwn2022] and in the program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906].

The framework's standards also provide a mechanism to assess the extent to which ready4 meets explicit accountability, reusability and updatability goals.

Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We  are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022].

 <!-- - One shot at big changes -->
 <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
 <!-- A coding framework for MOSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->

However, the framework represents a technical capacity and is not a behavioural outcome. Having features to facilitate accountability, reuse and updating does not guarantee being that our OSHEM will be meaningfully held accountable, reused and updated. Making code and data publicly available may make limited impact on error detection unless third parties begin to use these artefacts in their own projects. Currently all the framework and module libraries we have developed are available only as "development" releases. Further development, testing and documenting before we submit production versions of each library to the Comprehensive R Archive Network (CRAN) [@CRAN2022]. Having these libraries available on CRAN is a likely prerequisite of significant levels of reuse.

Estimating the potential uptake of these tools is difficult. Mental health topics accounted for about 268 of 2829 (10%) economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic].

Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@nmhsmn2022].

@@

## Implications for research funders
<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." -->

@@

The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve their validity over time. Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111]. For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42]. There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

>>>>

In this article we described a framework that we developed to help us implement ready4 - a MOSHEM in youth mental health. We outlined framework standards for an accountable, reusable and updatable MOSHEM and described the modelling toolkit we created for applying those standards to the development and use of the ready4 MOSHEM. We also provided an overview of an initial set of MOSHEM modules developed with the framework to implement a utility mapping study. We reviewed the modules, datasets and analyses generated by that study against framework standards. The work we have described has potential implications for the development of the ready4 MOSHEM and for health economic modelling in mental health and highlights more general issues for health economic modellers and funders of health economic research.

## Implications for implementing ready4
The most direct implication of the development of the ready4 framework is that it makes it feasible for us to implement a MOSHEM in youth mental health. The standards specified by the framework have enabled us to partially automate workflows for developing and applying ready4 through use of the framework's modelling toolkit. We have demonstrated the practical utility of the modelling toolkit by applying it to authoring, documenting and disseminating ready4 module libraries  [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155], datasets [@DVN/HJXYKQ_2021; @DVN/DKDIB0_2021]; analyses [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], reporting templates [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and prediction tools  @matthew_p_hamilton_2021_5646669] used in a utility mapping study [@Hamilton2021.07.07.21260129]. The standardised and partially automated workflows used in creating and sharing these artefacts has the potential to generate significant efficiencies as we apply the ready4 framework to undertaking new studies.

We have also been able to demonstrate the interoperability of the initial ready4 modules developed with the modelling toolkit. The program used to implement the utility mapping analysis [@hamilton_matthew_2022_6129906] combines modules from four module libraries ([@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155]) and two framework libraries [@ready4use2022; @ready4show2022]. Example literate programs published on the ready4 documentation website [@rfwn2022] use toy data [@DVN/HJXYKQ_2021] to illustrate the potential for ready4 modules to facilitate study replication and transferability. The framework's standards also provide a mechanism for to assess the extent to which the ready4 MOSHEM meets explicit accountability, reusability and updatability goals.

However, having features that facilitate accountability, reuse and updating is not the same as being accountable, reused and updated. If diverse groups of stakeholders do not review model components, suggest improvements and develop alternatives, then little progress is made towards enhancing model legitimacy. Similarly, making code and data publicly available does not guarantee that others will know of the existence of these tools, trust their validity and find them easy to use. Without reuse, errors in model aretefacts are more likely to remain undetected. Even when errors are detected, they still need to be fixed, but maintaining code and data requires ongoing resourcing through a combination of centralised infrastructure and an active open source community.

Currently all the framework and module libraries we have developed are available only as "development" releases. An early priority for us is to undertake the additional development, testing and documenting of these libraries so that we can submit production versions of each library to CRAN [@CRAN2022]. Making these libraries available on CRAN is a likely prerequisite of high levels of reuse. Similarly, completing our current work program will create new tools for modelling help-seeking choice, spatial epidemiology, household populations and primary mental health services that may enhance the potential usefulness of the ready4 MOSHEM to health economists working in youth mental health.

## Implications for economic modelling in mental health
Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. We are aware of just one other open source mental health model - a reference model in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. Of the known barriers to adoption of open source models by health economists (including issues like intellectual property and confidentiality [@Pouwels2022; @Wu2019]), our experience suggests that the enormous effort that is required to prepare model code and data for public release in formats that facilitate appropriate reuse by third parties and to maintain and improve these artefacts may be the biggest challenge.

Automated tools such as those we developed in our modelling toolkit can help reduce the burden of some of these tasks. However, we think the current low rates of adoption by health economists of open source approaches [@Emerson2019; @Michalczyk2018; @Feenstra2022] (which in turn facilitate the collaboration that make modular models more attractive) is unlikely to change soon without significant and strategic changes by research funders. The incentive structures that health economists work within do not promote the investment of significantly more time on each study to enable peers to reuse their work.

Reducing waste in research is a responsibility of research funders [@chalmers2014increase] and the poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017], limited reusability [@Emerson2019; @Michalczyk2018; @Feenstra2022] and uncertain validity [@Ghabri2019; @Radeva2020] of health economic models is wasteful. Approximately 4,000 mental health focused economic evaluation reports were produced between 2000 to 2019 [@RN34]. The intellectual asset represented by this literature could be very substantial if many of the models described in these reports could be brought (and kept) up to date and made available in formats that maximised transferability to diverse decision contexts. We believe that modular and open source approaches would be well suited to accomplishing this goal and that the framework we have developed could act as an early prototype for solving some of the technical challenges of this task. Ideally such a programme of research would be resourced to be sustained over the medium to long term and to engage a diverse network of investigators, contributors and advisers from high, middle and low income countries.

In addition to extracting more value from the existing health economic knowledge base in mental health, there is an opportunity for research funders to shape how future health economic models in mental health are undertaken. Mental health topics accounted for about 268 of 2829 (10%) peer reviewed economic evaluations undertaken during 26 month period in 2012-2014 identified in a previous review [@pitt2016economic]. There is also likely to a substantial annual output of economic research in mental health that focuses on the other 11 domains identified by Wagstaff and Culyer [@wagstaff2012four].

Providing adequate levels of funding to support MOSHEMs, fostering skills, supplying infrastructure (t)

Developing networks of modellers working on common health conditions has been recommended as a strategy for improving model validity [@Sampson2019] and some of us are part of a nascent initiate of this type in mental health [@whiteford_bagheri_2022]. Collaboration between teams of health economists can make some complex modelling projects more feasible [@Arnold2010] and the significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there are a number of candidate topics in mental health that might benefit from pooling of efforts. The weak theoretical underpinnings for understanding complex mental health systems [@RN2111] may be a place to start. It remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The  literature, and evidence base, regarding how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42]. There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->
<!-- http://hdl.handle.net/1893/27205--><!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." --

<!-- the framework represents a technical capacity rather than a behavioural outcome.  -->

<!-- (described in more detail on the project documentation website [@rfwn2022])  -->

 <!-- - One shot at big changes -->
 <!-- - Our analysis - do it in stages, be transparent, continually improve, get help, be flexible (modelling toolkit / monolithic model), have a framework -->
 <!-- A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019]. -->

<!-- Is it desirable for this to become default authoring tool or better to be replication tool. -->

Estimating the potential uptake of these tools is difficult.

@@

## Implications for research funders
<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
>

@@

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
section 2 of disc

We applied the framework to develop ready4 modules for developing utility mapping models, supplying those modules with data and implementing utility mapping analyses. These tools were created to develop utility mapping models for a clinical mental health sample of young people in a study that has been previously described [@Hamilton2021.07.07.21260129]. The framework's modelling toolkit created the following ready artefacts:

@@

When we assesses these study outputs against each framework standard, we conclude that 18 out of 20 standards were wholly or mostly met (see Table \@ref(tab:checktb)). The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface. Both these items are scheduled to be addressed when we release production versions of the code libraries.

>>>>

We applied the ready4 framework to develop an initial set of MOSHEM modules, supplying those modules with data and implementing analyses. These tools were created as part of a previously described study [@Hamilton2021.07.07.21260129] to develop utility mapping models appropriate for use in samples of young people presenting to primary mental health services. The ready4 framework's modelling toolkit created the following artefacts:

@@

We assess that these study outputs either wholly or mostly meet 18 out of 20 framework standards(see Table \@ref(tab:checktb)). The two standards where the study outputs currently fall short are in reporting code coverage and including a user-interface. Both these items are scheduled to be addressed when we release production versions of the code libraries.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
section 2 of disc

Based on published guidance on computational modelling in health economics and other disciplines as well as our own experience in developing ready4, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). The standards are specified in Table \@ref(tab:timelygls) and are discussed below.

@@

The coding practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022]. In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects. The coding concept of inheritance [@8717448] can be used to efficiently achieve this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022]. Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. Functions to implement model algorithms can be associated with module data structures (also known as a class) via a special type of function called a method. Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries. It is good practice to make available test or toy data to demonstrate the use of model algorithms [@Wilson_2017].

Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.

### Standards for an updatable MOSHEM
To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].

>>>>

Based on published guidance on computational modelling in health economics and other disciplines as well as our own experience, we have identified 20 standards that we believe are important for implementing a MOSHEM that is accountable (seven standards), reusable (nine standards) and updatable (four standards). The standards are specified in Table \@ref(tab:timelygls) and are discussed below.

@@

The software development practice of encapsulation [@8717448] can be used to help ensure that model modules continue to work as intended when they are combined [@ready4oop2022]. In some cases, combining modules may mean new versions of modules have to be created to better account for interaction effects. The concept of inheritance [@8717448] can be used to write code that efficiently achieves this objective as well as to facilitate selective editing of modules when transferring models to different decision contexts [@ready4oop2022]. Writing algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. Functions to implement model algorithms can be associated with data structures (also known as a class) via a special type of function called a method. Model modules of a similar type or purpose can be efficiently distributed and documented by bundling them as code libraries. It is good practice to make available test or toy data to demonstrate the use of model algorithms [@Wilson_2017].

Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them for out of sample prediction [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make MOSHEMs easier to use is to develop simple user-interfaces for non-technical users.

### Standards for an updatable MOSHEM
To avoid MOSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020] such as [@git20XX].

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
section 2 of disc

We developed a toolkit to help us develop and use ready4 modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls). The toolkit is comprised of online repositories and software.

## Repositories <!-- Existing ref -->
We created a GitHub organisation (a collection of code repositories) where all our development code is stored and version controlled [@ready4gh2022]. We linked our GitHub organisation to an account we established at codecov [@codecov_2022] to track our code coverage. We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration.

For hosting documentation websites for the code libraries we create, we enabled GitHub Pages in each library's repository. We also developed a consolidated project documentation website [@rfwn2022], using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023]. To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.

We also created a Zenodo community [@ready4zen2022] - a collection of permanent, unbiquely identified repositories. We then linked our Zenodo community and GitHub organisation so that every time we create a new "release" in a GitHub repository, a copy of that code is automatically created on Zenodo with a DOI. Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation [@ready4dv2022].

@@

The foundation for ready4 is provided by a library called ready4 [@ready42022] that defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules. The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project website.

Three R libraries are designed to standardise and partially automate workflows for authoring new model modules. The ready4pack library [@ready4pack2022] provides tools for authoring module libraries that are:

@@

The ready4pack library is designed to integrate with our GitHub organisation and depends on two other module authoring libraries. Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style. The standardised format is then used by ready4fun to automatically generate basic documentation for each function. Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data-structures. Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data-structure.

>>>>

We developed a toolkit to help us develop and use MOSHEM modules, datasets and analyses that meet the standards listed in Table \@ref(tab:timelygls). The toolkit is comprised of online repositories and software.

## Repositories <!-- Existing ref -->
We created a GitHub organisation (a collection of code repositories) where all our development code is stored and version controlled [@ready4gh2022]. We linked our GitHub organisation to an account we established at codecov [@codecov_2022] to track our code coverage. We configured the repositories in our GitHub organisation to use GitHub actions to support continuous integration. Some of the continuous integration checks we have defined assess each library's compliance with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022], to which we plan submitting future production releases.

For hosting documentation websites for the code libraries we create, we enabled GitHub Pages in each library's repository. We also developed a consolidated and versioned project documentation website [@rfwn2022], using the Hugo framework [@hugo_2023] and Docsy theme [@docsy_2023]. To host that website we established an account with Netlify [@netlify_2023] and linked that service to our GitHub organisation so that the website would automatically update whenever the source code in its GitHub repository was edited.

We also created a Zenodo community [@ready4zen2022] - a collection of permanent, uniquely identified repositories. We then linked our Zenodo community and GitHub organisation so that every time we create a new "release" in a GitHub repository, a copy of that code is automatically created on Zenodo with a DOI. Finally, to manage model datasets, we created a dedicated collection within the Harvard Dataverse installation [@ready4dv2022].

@@

A library called ready4 [@ready42022] defines a template module (using R's S4 type class) from which all model module data structures will inherit features and a novel syntax for implementing the algorithms attached to model modules. The ready4 library also contains tools for retrieving web based information on model modules, datasets and analysis programs and for partially automating updates to the project website.

Three R libraries are designed to standardise and partially automate workflows for authoring new model modules. The ready4pack library [@ready4pack2022] is designed to integrate with our GitHub organisation and provides tools for authoring module libraries that are:

@@

The ready4pack library depends on two other module authoring libraries. Methods from the ready4fun library [@ready4fun2022] are used to verify that functions for implementing module algorithms are written in a consistent house style. That standardised format is then used by ready4fun methods to automatically generate basic documentation for each function. Methods from the ready4class [@ready4class2022] library are used to streamline and standardise the authoring of module data structures and the linking of methods to these data structures. Like ready4fun, the ready4class library uses standardised code implementation to automatically generate basic documentation for each module data structure.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
section 2 of disc

A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular]. Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], neuroscience [@frazier2022robust] and ecology [@barros2023empowering]. In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].

@@

- *determinants of health and ill-health* (our projects: models for creating rich and representative synthetic household populations from survey data);

@@

- *economic evaluation* (our goal: assess the cost-utility of competing policy options).

To undertake this work we first needed to develop a framework for standardisation. Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches. However, MOSHEMs remain rare and is unclear what standards are most appropriate to specify. A MOSHEMs is a computational modelling project, so standards developed for ready4 will need to be verified and implemented by software, some of which will need to be developed for this specific purpose.

>>>>

A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular]. Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust]. In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].

@@

- *determinants of health and ill-health* (our projects: models for creating synthetic household populations with key risk and protective factors for mental disorders);

@@

- *economic evaluation* (our goal: assess the cost-utility of competing policy options for improving the mental health of young people).

Standardisation is an essential enabler of automation, collaboration, interoperability and transferability in modular and open source approaches. An early requirement to implement ready4 is therefore to identify an appropriate set of standards. However, we are not aware of any consolidated source of guidance about recommended standards for MOSHEMs. Once identified, the standards specified for ready4 will need to be implemented by software, some of which will require custom development.

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
wip on discussion
section 2 of disc

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->
# Framework
<!-- Modular and open source models from other disciplines are enabled by standardisation and software.  -->
To help us implement a MOSHEM in youth mental health, we have developed a framework that:

>>>>

```{r child="../Child_RMDs/XX_Funs.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Tables.Rmd", echo=FALSE}
```
```{r child="../Child_RMDs/MS_Figures.Rmd", echo=FALSE}
```
<!-- Add child RMDs for results content -->
# The ready4 framework
<!-- Modular and open source models from other disciplines are enabled by standardisation and software.  -->
To enable us to implement ready4, we have developed a framework that:

### 2023-01-31 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
section 2 of disc

                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures. It was created to demonstrate generalised applications of study algorithms.",                                           #

@@

                                           "Retired code is deprecated using tools from the lifecycle R library [lifecycle2021] (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"

>>>>

                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_tb.Rds) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures. It was created to demonstrate the transferability of study algorithms.",                                           #

@@

                                           "Retired code is deprecated using tools from the lifecycle R library [@lifecycle2021] (e.g. everything after “## DEPRECATED FNS” in https://github.com/ready4-dev/youthvars/blob/main/data-raw/fns/add.R ). Package vignettes and datasets are also deprecated e.g. https://ready4-dev.github.io/youthvars/articles/Replication_DS.html )"
